Comparing OTU quality across clustering strategies

### 2021-10-22 exploratory/2021/seq_stats.Rmd
Make a table of quantiles

```{r dat}
seq_stats <- c("human","marine","mouse","soil") %>% map_dfr(function(x) {
  read_tsv(glue('subworkflows/1_prep_samples/data/{x}/seq_stats.tsv')) %>% 
    mutate(dataset = x)
}) %>% pivot_longer(c(similarity, abundance), names_to = 'statistic')
```

@@

```{r hist_sim_abun_log10}
seq_stats %>% 
  ggplot(aes(x=value, fill=statistic)) +
  geom_histogram() +
  scale_x_log10() +
  facet_wrap("dataset")
```

@@

rel_stats <- c("human", "marine", "mouse", "soil") %>% map_dfr(function(x) {
  read_tsv(glue('subworkflows/1_prep_samples/data/{x}/seq_stats.tsv')) %>% 
    mutate(dataset = x,
           rel_sim = similarity / (totals %>% 
                                     filter(dataset == x) %>% 
                                     pull(tot_simi)),
           rel_abun = abundance / (totals %>% 
                                     filter(dataset == x) %>% 
                                     pull(tot_abun))
           )
})
```

@@

>>>>

```{r dat}
dataset_names <- c("human","marine","mouse","soil")
seq_stats <- dataset_names %>% map_dfr(function(x) {
  read_tsv(glue('subworkflows/1_prep_samples/data/{x}/seq_stats.tsv')) %>% 
    mutate(dataset = x)
}) %>% pivot_longer(c(similarity, abundance), names_to = 'statistic')
```

@@

```{r hist_sim_abun_log10}
seq_stats %>% 
  ggplot(aes(x=value, fill=statistic)) +
  geom_histogram() +
  scale_x_log10() +
  facet_wrap("dataset")
```
```{r hist_sim_abun_log10bins}
seq_stats %>% 
  ggplot(aes(x=value, fill=statistic)) +
  geom_histogram(bins=10) +
  scale_x_log10() +
  facet_grid(dataset ~ statistic, scales='free')
```

@@

rel_stats <- dataset_names %>% map_dfr(function(x) {
  read_tsv(glue('subworkflows/1_prep_samples/data/{x}/seq_stats.tsv')) %>% 
    mutate(dataset = x,
           rel_sim = similarity / (totals %>% 
                                     filter(dataset == x) %>% 
                                     pull(tot_simi)),
           rel_abun = abundance / (totals %>% 
                                     filter(dataset == x) %>% 
                                     pull(tot_abun))
           )
})
```

@@

```{r quantiles}
quantile_custom <- function(x, by = 0.05) {
  x %>% 
    quantile(., seq.int(from = 0.1, to = 1, by = by))
}
get_quantile <- function(dat, dataset_name, var = abundance) {
  quantiles <- dat %>% 
    filter(dataset == dataset_name) %>% 
    pull({{ var }}) %>%  
    quantile_custom()
  data.frame(quant = names(quantiles), 
             value = quantiles, 
             row.names = NULL) %>% 
    mutate(dataset = dataset_name)
}
get_dataset_quantiles <- function(dat, column = abundance) {
  dataset_names %>% 
    map_dfr(function(x) {get_quantile(dat = dat, 
                                    dataset_name = x,
                                    var = {{column}})
                         }) %>% 
    pivot_wider(names_from = dataset, values_from = value) 
}
```

### abundance quantiles

```{r abun_quant}
rel_stats %>% 
  get_dataset_quantiles(column = abundance) %>% 
  knitr::kable()
```

### similarity quantiles

```{r simi_quant}
rel_stats %>% 
  get_dataset_quantiles(column = similarity) %>% 
  knitr::kable()
```
